### 2020-01-08 Paper_EV/Paper_EV.tex
Paper_EV: NDI chapter added

@@

% Package for acronyms
\usepackage[acronym, automake, nopostdot, nogroupskip]{glossaries}
\setlength{\LTleft}{-0.15cm}			% left justified
\renewcommand*{\arraystretch}{1.4}		% vertical distance between entries, default is 1
% List
\newacronym{ADF}{ADF}{Automatic Direction Finder}
\newacronym{ADI}{ADI}{Automatic Direction Indicator}
% Make gls
\renewcommand*\entryname{Acronym}
\makeglossaries

@@

- Theory from Sieberling paper.

>>>>

% Package for bold symbols and letters
\usepackage{bm}

% Package for equations
\usepackage{amsmath}

@@

% Package for acronyms
\usepackage[acronym, automake, nopostdot, nogroupskip]{glossaries}
\setlength{\LTleft}{-0.15cm}			% left justified
\renewcommand*{\arraystretch}{1.4}		% vertical distance between entries, default is 1
% List
\newacronym{NDI}{NDI}{Nonlinear Dynamic Inversion}
\newacronym{INDI}{INDI}{Incremental Nonlinear Dynamic Inversion}
% Make gls
\renewcommand*\entryname{Acronym}
\makeglossaries

@@

In this subsection, the \acrfull{NDI} method is explained. \acrshort{NDI} is based on feedback linearization and is also called \textit{Input-Output Linearization}. This method is often involved in tracking control tasks, where objective is to track some desired trajectory. (cite-tag Slotine) To show it in practice, consider following nonlinear system
\begin{subequations}
	\begin{align}
		&\bm{\dot{x}} = \bm{f(x)} + \bm{G(x)}\bm{u} \\
		&\bm{y} = \bm{h(x)}
		\label{eq:nonlin_sys}
	\end{align}
\end{subequations}
where $\bm{x}$ is the $n\times1$ state vector, $\bm{u}$ the $m\times1$ input vector, $\bm{y}$ the $m\times1$ system output vector, $\bm{f(x)}$ and $\bm{h(x)}$ nonlinear vector fields and $\bm{G}$ an $m\times n$ matrix. Note that the system presented in Equation (\ref{eq:nonlin_sys}) is affine in the input, which is not allways the case. To deal with this problem the system can be transformed into nonlinear normal (canonical) form through the state transformation.

The idea behind the input-output linearization method is to find a direct relationship between the desired system output and the control input and then invert it. To generate this relationship the output $\bm{y}$ is differentiated until the input $\bm{u}$ appears
\begin{equation}
	\begin{split}
		\dot{\bm{y}} &=  \frac{\partial\bm{y}}{\partial t} = \frac{\partial\bm{h(x)}}{\partial t} \frac{\partial\bm{x}}{\partial t} = \frac{\partial\bm{h(x)}}{\partial t} \dot{\bm{x}} = \nabla\bm{h(x)} [\bm{f(x)} + \bm{G(x)}\bm{u}] \\
		&= \nabla\bm{h(x)} \bm{f(x)} + \nabla\bm{h(x)} \bm{G(x)}\bm{u}] = L_{\bm{f}} \bm{h(x)} + L_{\bm{G}} \bm{h(x) u} 
		\label{eq:dy}
	\end{split}
\end{equation}
In Equation (\ref{eq:dy}) $L_{\bm{f}} \bm{h(x)}$ is called Lie derivative of $\bm{h(x)}$ with respect to $\bm{f(x)}$. The Lie derivative is defined as $L_{\bm{f}} \bm{h(x)} = \nabla\bm{h(x)} \bm{f(x)}$ with $\nabla$ being the Nabla operator. Thus, it represents a directional derivative of $\bm{h(x)}$ along the direction of the vector field $\bm{f(x)}$. If the term $L_{\bm{G}} \bm{h(x) u}$ is not zero, the relationship between input and output is
\begin{equation}
	\begin{split}
		\dot{\bm{y}} = L_{\bm{f}} \bm{h(x)} + L_{\bm{G}} \bm{h(x) u} 
		\label{eq:dy_u_rel}
	\end{split}
\end{equation}

Now Equation (\ref{eq:dy_u_rel}) can be used to formulate the control law by solving it for $\bm{u}$ and substituting $\dot{\bm{y}}$ with $\bm{\nu}$
\begin{equation}
	\begin{split}
		\bm{u} = L_{\bm{G}}\bm{h(x)}^{-1} (\bm{\nu} - L_{\bm{f}}\bm{h(x)})
		\label{eq:u_control_law}
	\end{split}
\end{equation}
The variable $\bm{\nu}$ is called an \textit{equivalent input}. It represents the desired output of the system.

In the example provided above the input-output relationsip was found after the first differentiation of the output. If this is not the case and the term $L_{\bm{G}}\bm{h(x)}$ is zero, output $\bm{y}$ has to be differentiated until the Lie derivative with respect to $\bm{G}$ is nonzero
\begin{equation}
	\begin{split}
		\frac{\partial^i\bm{y}}{\partial t} = \frac{\partial^i\bm{h(x)}}{\partial t} = L_{\bm{f}}^i \bm{h(x)} + L_{\bm{G}} L_{\bm{f}}^{i-1} \bm{h(x) u}
		\label{eq:dy_i}
	\end{split}
\end{equation}
with $i$ being the \textit{relative degree} of the system. Using Equation (\ref{eq:dy_i}) to formulate the control law, leads to the following expression for $\bm{u}$
\begin{equation}
	\begin{split}
		\bm{u} = L_{\bm{G}} L_{\bm{f}}^{i-1} \bm{h(x)}^{-1} (\bm{\nu} - L_{\bm{f}}^i\bm{h(x)}) 
		\label{eq:u_control_law_i}
	\end{split}
\end{equation}
Equation (\ref{eq:u_control_law_i}) applied to Equation (\ref{eq:dy_i}) yields the simple linear relation
\begin{equation}
	\begin{split}
		\bm{y}^i = \bm{\nu}
		\label{eq:u_control_law_i}
	\end{split}
\end{equation}
Despite wide usage (especially in the past of the flight control design) of the \acrshort{NDI} method and its numerrous extensions (cite-tag Horn), it also has drawbacks. The major one is that the control law derived with \acrshort{NDI} is dependend on the dynamics model and its uncertainties. As shown in the previous chapter (cite-tag prev-chapter), the equations of motion of an aircraft usually have a complicated nonlinear character. Thus, creating a perfectly aqurate model of the aircraft is not an easy task. To overcome this obstacle an extension of the \acrshort{NDI} method called \acrshort{INDI} can be incorporated.
